Homicide Increases in the COVID-19 Era

### 2025-02-27 Draft1.qmd
updated code

# Secondary dataset - Median Income by ZCTA
california_median_income_2018_2023 <- list()
yrs <- 2018:2023
for (i in 1:length(yrs)) {
  obj <- read.csv(paste0("Raw_Data/ACSST5Y",yrs[[i]],".S1903-Data.csv"), skip = 0)
  obj <- obj[-1,]
  obj$year <- yrs[[i]]
  california_median_income_2018_2023[[i]] <- obj
}

cali_median_income <- read.csv("Cleaned_Data/cali_median_income.csv")

>>>>

# Secondary dataset - Median Income by ZCTA
cali_median_income <- read.csv("Cleaned_Data/cali_median_income.csv")
